[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-17 analysis/paper.Rmd
adding reference to original paper
converted cleaning and visuals to tidyverse

``` {r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures")
#knitr::read_chunk("src/my-external-code.R")
```

@@

Reference 1: @marriagehappiness  
Reference 2: @data

>>>>

``` {r setup, echo = FALSE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures")
#knitr::read_chunk("src/my-external-code.R")

# load packages
library(tidyverse)
library(gssr)
```

```{r get_data, echo = FALSE}
# ==== Get Data
# The happiness, race, and marital data comes from the gssr package and not the provided data since the provided version
  # does not have race or marital status. For more information, go to https://kjhealy.github.io/gssr/
data(gss_all)

# The Gini indices come from the provided dataset
gini <-  read.csv("../data/Gini_families.csv") %>%
  select(year = Year, gini = Total)

# ==== Clean data
# Subset the GSS data to just the relevant fields
gss <- gss_all %>%
  select(year, happy, race, marital) %>%
  mutate(year = as.integer(year), # fix data class
         happy = as.integer(happy),
         happy = recode(happy, `1`= 3, `2` = 2, `3` = 1), # reverse the values such that higher is more happy
         race = as.integer(race),
         marital = as.integer(marital)) %>%
  na.omit() # remove NAs (4780/64,814 cases where not all data was collected)

# join the gini and happiness/race/marital data
happy <- gini %>%
  left_join(gss, by = c("year" = "year")) %>%
  na.omit()

# create summary table by year
happy_race_summary <- happy %>%
  group_by(year, race) %>%
  summarize(happy_avg = mean(happy))

# write a function

```{r plots}
g <- ggplot(happy_race_summary, aes(x = year, y = happy_avg, color = factor(race)))
g + geom_point() +
  geom_line(stat = "smooth",
            method = "lm", 
            se = FALSE, 
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Figure 3",
       x = "Year",
       y = "Mean Happiness",
       caption = "Figure 3") +
  scale_color_discrete(name="Race",
                      breaks=c(1, 2, 3),
                      labels=c("White", "Black", "Other")) +
  scale_y_continuous(limits = c(1.9,2.5))

A reference implementation of:

> Grunberg, Rebecca L., Hyejun Kim, and Minjae Kim. 2014a. “Marriage and Happiness Grunberg Kim Kim.pdf.” Harvard Dataverse. https://doi.org/10.7910/DVN/25655/MB980L

Which is a reference implementation of:

> Oishi, S., Kesebir, S., & Diener, E. (2011). Income Inequality and Happiness. Psychological Science, 22(9), 1095–1100. https://doi.org/10.1177/0956797611417262

@@

Reference 1: @marriagehappiness  
Reference 2: @data
Reference 3: @incomeinequality
